\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{Alegreya} % Original font choice
\usepackage{xcolor} % For color
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{setspace} % For line spacing
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % Set to true to disable boxes and color the text instead
    linkcolor=blue,   % Color of internal links
    urlcolor=subtlered,    % Color of external URLs
    citecolor=red    % Color of citations
}


% Define colors
\definecolor{subtlered}{RGB}{156,31,46}

\geometry{a4paper, margin=20mm, bottom=25mm}
\titleformat{\section}{\large\bfseries\color{subtlered}}{}{0em}{}[\titlerule] % Section formatting with subtle red color
\setlength{\parindent}{0pt}
\setstretch{1.1} % Line spacing

% Header and Footer Configuration
\fancyfoot[C]{\thepage}
\pagestyle{fancy}
\setlength{\headheight}{13.6pt} % Adjust head height as per warning

\begin{document}

\thispagestyle{empty}

% Header
\begin{center}
    {\Huge\bfseries Siddharth Nair}\\[2mm]
    \small \href{tel:+447387653642}{07387653642} $\cdot$ \href{mailto:ambiverb@gmail.com}{ambiverb@gmail.com} $\cdot$ \href{https://github.com/essentialblend}{github.com/essentialblend}\\[4mm]

    % Personal Statement
    \noindent\begin{minipage}{\textwidth}
    \normalsize
    \textit{Versatile computer scientist with a background in computer graphics, computational optimization, type theory, and gameplay programming. Enthusiastic about continually learning and applying concepts encompassing myriad fascinating fields like mathematics, physics, games, and music.}
    \end{minipage}\\[2mm]
\end{center}

% Education Section
\section*{Education}
\textbf{University of Nottingham, --- MSc Computer Science (2:2 -- 3.3 of 5)} \hfill 2022 - 2023\

Memberships: Art and Chess Societies.\

Key Modules:
\vspace{-2mm}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Computer Graphics (70\%)
    \item Programs, Proofs, and Types (82\%)
    \item Linear and Discrete Optimization (60\%)
    \item Programming (68\%)\
    \vspace{2mm}
    \item Research Project (70\%): "The Commutative Ring of Integers: Formal Constructive Proofs for Algebraic Properties with Agda and Type Theory"
    \begin{itemize}[leftmargin=*, noitemsep]
    \item Developed constructive proofs for abstract algebraic structures.
    \item Analysed various approaches for building and representing integers within the intuitionistic logic framework.
    \item Demonstrated the utility and flexibility of proof assistants to aid formalization.
    \end{itemize}
\end{itemize}

\vspace{2mm}
\textbf{CMR University,--- BCA Games and Mobile Software Development (4.4 of 5)} \hfill 2018 - 2021\

Key Modules: Game Development with Unity and Unreal Engine, Mobile Applications with Android Studio, C++/C\#, and Java Programming.\
\vspace{2mm}

\textbf{SAE University,--- Diploma in Audio Engineering (3.5 of 5)} \hfill 2010 - 2012\

Key Modules: Music Production with Logic and Pro Tools, Live Production, Acoustics.\

% Technical Skills Section
\section*{Technical Skills}
\begin{itemize}[leftmargin=*, noitemsep]
\item \textbf{Programming Languages:} C++, glsl, python.
\item \textbf{Software:} Agda, Visual Studio, Unreal Engine, LaTeX, Excel, LP-Solve, Renderdoc, Ableton.
\item \textbf{Source Control:} Git, Perforce.
\item \textbf{Graphics APIs:} OpenGL.
\item \textbf{Mathematics:} Linear algebra, Euclidean geometry, one variable calculus, lambda calculus, combinatorics, axiomatic, and intuitionistic logic.
\item \textbf{Linear and Discrete Optimization:} Algebraic models, network flow optimization, post-optimality analysis, multi-objective and combinatorial optimization, Simplex, and Branch and Bound.
\item \textbf{Machine Learning:} Elementary familiarity with concepts such as regression, SVMs, neural networks etc.
\end{itemize}

% Work Experience Section
\section*{Work Experience}

\textbf{Audio Engineer,-- GTPL Hathway} \hfill Gujarat, India\\
\textit{March 2018 - August 2018}

\begin{itemize}[leftmargin=*, noitemsep]
    \item Managed audio production for live and in-studio broadcast events for a state-wide news-station.
    \item Programmed and deployed programmes from ads to pre-scheduled telecasts, as part of the core PCR team.
\end{itemize}

\textbf{Audio-Video Producer,-- Chrysalis Comms.} \hfill Gujarat, India\\
\hfill\textit{January 2015 - January 2018}

\begin{itemize}[leftmargin=*, noitemsep]
    \item Involved with pre-production and audio-video editing for infomercials produced for the state government and various organizations.
    \item Produced audio and foley for on-location shoots and post-production duties.
    \item Collaborated with relevant stake-holders to aid product execution.
\end{itemize}

% Projects Section
\section*{Projects}
\textbf{Graphics:}
\begin{itemize}[leftmargin=*, noitemsep]
\item \textbf{Rasterizer in C:} Programmed a software rasterizer in C with super-sampled anti-aliasing.
\item \textbf{3D Prototype in OpenGL:} A 3D application where I implement and demonstrate:
\begin{itemize}[leftmargin=*, noitemsep]
\item OpenGL fundamentals including some utilities such as an .obj parser, maps, etc.
\item Blinn-Phong lighting, shadow mapping and filtering techniques for directional, spot, and point sources alongside normal maps.
\item Screen-space and post-process effects such as god-rays, aberration, fog etc.
\item Procgen with algorithms like Fractal Brownian Motion.
\end{itemize}
\item \textbf{Game of Life in OpenGL:} The classic cellular automata where I implement:
\begin{itemize}[leftmargin=*, noitemsep]
\item Modern OpenGL using DSA.
\item Parallelized gameplay logic using compute shaders.
\item Core gameplay mechanics such as grid handling and generation.
\end{itemize}
\end{itemize}

\textbf{Computational Optimization:}
\begin{itemize}[leftmargin=*, noitemsep]
\item Programmed and optimized algebraic models for diet optimization, network flows, task assignment, scheduling, bin-
packing, travelling salesmen, facility location, vehicle routing and other related problems. 
\item Demonstrated approaches for modelling and optimization using Excel, and LP-Solve.
\end{itemize}

\textbf{Gameplay Programming:}
\begin{itemize}[leftmargin=*, noitemsep]
\item \textbf{C++ First-Person Shooter Prototype:} A C++ + Blueprints prototype demonstrating various shooter archetypal gameplay mechanics such as traversal, projectiles, UX, AI etc.
\item \textbf{TanksShooter Demo:} A simple tank shooter testing basic gameplay programming with Unreal Engine 4.
\item \textbf{PRTCL:} A PVP lighting and destruction based prototype demonstrating mechanics with Unity.
\item \textbf{Game Audio:} Composed/produced sfx and soundtracks for multiple student projects showcased at IGDC.
\end{itemize}

% Development
\section*{Ongoing Professional Development}
\begin{itemize}[leftmargin=*, noitemsep]
\item \textbf{Physics:} University Physics with Modern Physics by Young \& Freedman covering Newtonian Dynamics (notes and solutions on git), Six Easy Pieces by R.Feynman.
\item \textbf{Mathematics/Type Theory:} Apostol's Calculus (nearing Vol I completion), Homotopy Type Theory, Euclid's Elements (covered 3 of the first core 6 volumes).  
\item \textbf{Graphics Programming:} Vulkan, Renderdoc.
\item \textbf{Machine Learning:} The 100 Page ML Book.
\item \textbf{History:} The History of the Ancient World by S.W.Bauer, Mathematics: From the Birth of Numbers by J.Gullberg.
\end{itemize}

\section*{Extracurriculars}
\begin{itemize}[leftmargin=*, noitemsep]
\item \textbf{Music composition and production:}
\begin{itemize}[leftmargin=*, noitemsep]
\item I enjoy creating and producing music, especially with synths.
\item Formal education in western music theory from Trinity, completing 5 of 8 grades.
\item Varying levels of proficiency with instruments (guitars, tabla, recorder).\
\end{itemize}

\item \textbf{Misc:}
\begin{itemize}[leftmargin=*, noitemsep]
\item Games, history, stories, and terrariums.
 \item Watercolours, paints, and pigments. I studied various courses to learn how to paint, and learn about properties of pigments.
\item Volunteering experience at a wildlife sanctuary.
\end{itemize}
\end{itemize}

\section*{References}
Available upon request.

\end{document}
